---
title: "Local Regression"
date: 
output: 
  revealjs::revealjs_presentation:
    transition: none
    theme: solarized
    highlight: kate
    center: true
    fig_width: 12
    fig_height: 8
    self_contained: False
    reveal_plugins: ["menu",'zoom']
    reveal_options:
      slideNumber: true
    menu:
        side: right
---


```{r,echo=FALSE,results='hide',warning=FALSE,message=FALSE,cache=TRUE}
#install.packages('revealjs')
library('revealjs')
```

##  1. Data 
\
\

$$Y_i=sinX_i+\epsilon_i$$ \

$$X_i \sim \mbox{N}(0,2)$$ \
$$\epsilon_i\sim \mbox{N}(0,1)$$ \

## 2. Nadaraya-Waston kernel estimator 

```{r}
## kernel function
k_f=function(u){
  return(dnorm(u,0,1))}
```



```{r}

### Nadaraya-Waston-kernel-estimator
Nadaraya_Waston=function(X_new,h,k_f,X,Y){
  Y_new=0  
  for(i in 1:length(X_new)){
    Y_new[i]=(k_f((X_new[i]-X)/h)%*%matrix(Y,n,1))/sum(k_f((X_new[i]-X)/h))
  } 
  result=list(Y_new=Y_new,X_new=X_new,h=h)
  return(result)
}

```

## about n....


## n=50

```{r,echo=FALSE,warning=FALSE,message=FALSE}
n=50
X=rnorm(n,mean=0,sd=2)
e=rnorm(n,mean=0,sd=1)
Y=sin(X)+e  

plot(X,Y,xlab = "x",ylab = "Y",main = "Scatter plot(n=50)",xlim = c(min(X), max(X)),ylim=c(-6,6),pch=20)
eq = function(X){sin(X)}
curve(eq, from=min(X),to=max(X),add = TRUE,lwd=4,col='gray70')


h=c(1.5,1,0.5,0.1,0.05)
color=list('blue','indianred1','mediumorchid3','salmon3','bisque1')

for(j in 1:5){
  ##
  Y_new=0
  X_new=seq(min(X),max(X),0.1)
  
  NW=Nadaraya_Waston(X_new,h[j],k_f,X,Y)

  data=cbind(NW$X_new,NW$Y_new)[order(NW$X_new),]
  lines(data[,1],data[,2],col=color[[j]],lwd=2)
}



legend(2,-2, c("y=sin(X)",'h=1.5','h=1','h=0.5','h=0.1','h=0.05'),text.col=c('gray70','blue','indianred1','mediumorchid3','salmon3','bisque1'))

```

## n=100

```{r,echo=FALSE,warning=FALSE,message=FALSE}
n=100
X=rnorm(n,mean=0,sd=2)
e=rnorm(n,mean=0,sd=1)
Y=sin(X)+e  

plot(X,Y,xlab = "x",ylab = "Y",main = "Scatter plot(n=100)",xlim = c(min(X), max(X)),ylim=c(-6,6),pch=20)
eq = function(X){sin(X)}
curve(eq, from=min(X),to=max(X),add = TRUE,lwd=4,col='gray70')


h=c(1.5,1,0.5,0.1,0.05)
color=list('blue','indianred1','mediumorchid3','salmon3','bisque1')

for(j in 1:5){
  ##
  Y_new=0
  X_new=seq(min(X),max(X),0.1)
  
  NW=Nadaraya_Waston(X_new,h[j],k_f,X,Y)

  data=cbind(NW$X_new,NW$Y_new)[order(NW$X_new),]
  lines(data[,1],data[,2],col=color[[j]],lwd=2)
}



legend(2,-2, c("y=sin(X)",'h=1.5','h=1','h=0.5','h=0.1','h=0.05'),text.col=c('gray70','blue','indianred1','mediumorchid3','salmon3','bisque1'))
```

## n=200
```{r,echo=FALSE,warning=FALSE,message=FALSE}
n=200
X=rnorm(n,mean=0,sd=2)
e=rnorm(n,mean=0,sd=1)
Y=sin(X)+e  

plot(X,Y,xlab = "x",ylab = "Y",main = "Scatter plot(n=200)",xlim = c(min(X), max(X)),ylim=c(-6,6),pch=20)
eq = function(X){sin(X)}
curve(eq, from=min(X),to=max(X),add = TRUE,lwd=4,col='gray70')


h=c(1.5,1,0.5,0.1,0.05)
color=list('blue','indianred1','mediumorchid3','salmon3','bisque1')

for(j in 1:5){
  ##
  Y_new=0
  X_new=seq(min(X),max(X),0.1)
  
  NW=Nadaraya_Waston(X_new,h[j],k_f,X,Y)

  data=cbind(NW$X_new,NW$Y_new)[order(NW$X_new),]
  lines(data[,1],data[,2],col=color[[j]],lwd=2)
}



legend(2,-2, c("y=sin(X)",'h=1.5','h=1','h=0.5','h=0.1','h=0.05'),text.col=c('gray70','blue','indianred1','mediumorchid3','salmon3','bisque1'))

```

## remark 
<p align="left">The risk of the Nadaraya-Watson kernel estimator</p>
\
$$\tiny  R(\hat{r}_n,r)=\color{DarkRed}{\frac{h^4_n}{4}\left(\int x^2 K(X) dx\right)^2\int\left(r^{\prime\prime}(x)+\color{DarkOrange}{\overset{design \; bias}{\overset{\uparrow}{\color{DarkOrange}{2r^{\prime}(x)\frac{f^{\prime}(x)}{f(x)}}}}}\right)^2dx} + \frac{\sigma^2 \int K^2(x)dx}{n h_n}\int\frac{1}{f(x)}dx+O(n h_n^{-1})+O(h^4_n)
$$
<p align="left">

* $\small R(\hat{r}_n,r)\;$ will not converge to 0, when $\;\small n \to \infty$ \ 
<p></p>
<font size=5.8>
   + bias 跟 n 無關 \
   + $\small R(\hat{r}_n,r)\to\; 0\;$ , as $\;\small h_n \to 0\;$ and$\small\; nh_n\to\infty$ \
   + Use cross validation to choose $\;\small h$ \
   + leave-one-out  or  GCV  or  $\;\small h=C n^{-\frac{-1}{5}}$ \
</font>   
*  kernel estimators have high bias near the boundaries.\
<font size=5.8>
   * reduce these biases by using local ploynomial
   regression\
</font> 
</p>

## 3. Local ploynomial regression


```{r}
#### Local ploynomial regression
local_ploy_reg=function(X_new,k_f,h,X,Y,p){
  
  n=length(X)
  r_x=0
  for(i in 1:length(X_new)){
    
    #############################
    #   X_x   
    #   W_x  
    X_x=matrix(NaN,n,(p+1)) # X_x 
    W_x=diag(NaN,n,n) # W_x 
    
    
    for(r in 1:n){
      
      for(c in 1:(p+1)){
        X_x[r,c]=(((X[r]-X_new[i])^(c-1))/factorial(c-1))
      }
      
      W_x[r,r]=k_f((X[r]-X_new[i])/h)
    }  
    ##################################
    # 例外處理
    
    
    tryCatch({
      
      ### l(x).trans
      e_T=append(1,rep(0,p))
      l_X_T=e_T%*%solve(t(X_x)%*% W_x%*%X_x)%*%t(X_x)%*%W_x
      
      ### r(x)
      r_x[i]= l_X_T%*%Y
      
      ### L --smoothing matr
      
    },error = function(err) {
      print(paste("ERROR:  ",err)) 
      print(i)
    })
  }
  result=list(X=X,Y=Y,r_x=r_x,X_new=X_new)
  return(result)
}

```


##  about p... 

##  Local ploynomial regression (<font color=#800000>p=0</font>、n=50)

```{r,echo=FALSE,warning=FALSE,message=FALSE}

n=50
X=rnorm(n,mean=0,sd=2)
e=rnorm(n,mean=0,sd=1)
Y=sin(X)+e  
p=0

plot(X,Y,xlab = "x",ylab = "Y",main = "Scatter plot(n=50)",xlim = c(min(X), max(X)),ylim=c(-6,6),pch=20)
eq = function(X){sin(X)}
curve(eq, from=min(X),to=max(X),add = TRUE,lwd=4,col='gray70')


h=c(1.5,1,0.5,0.1,0.05)
color=list('blue','indianred1','mediumorchid3','salmon3','bisque1')

for(j in 1:5){
  ##
  Y_new=0
  X_new=seq(min(X),max(X),0.1)
  
  req=local_ploy_reg(X_new,k_f,h[j],X,Y,p)

  data=cbind(req$X_new,req$r_x)[order(req$X_new),]
  lines(data[,1],data[,2],col=color[[j]],lwd=2)
}


legend(2,-2, c("y=sin(X)",'h=1.5','h=1','h=0.5','h=0.1','h=0.05'),text.col=c('gray70','blue','indianred1','mediumorchid3','salmon3','bisque1'))

```

------

##  Local ploynomial regression (<font color=#800000>p=1</font>、n=50)

```{r,echo=FALSE,warning=FALSE,message=FALSE,results='hide'}

n=50
#X=rnorm(n,mean=0,sd=2)
#e=rnorm(n,mean=0,sd=1)
#Y=sin(X)+e  
p=1

plot(X,Y,xlab = "x",ylab = "Y",main = "Scatter plot(n=50)",xlim = c(min(X), max(X)),ylim=c(-6,6),pch=20)
eq = function(X){sin(X)}
curve(eq, from=min(X),to=max(X),add = TRUE,lwd=4,col='gray70')


h=c(1.5,1,0.5,0.1,0.05)
color=list('blue','indianred1','mediumorchid3','salmon3','bisque1')

for(j in 1:5){
  ##
  Y_new=0
  X_new=seq(min(X),max(X),0.1)
  
  req=local_ploy_reg(X_new,k_f,h[j],X,Y,p)

  data=cbind(req$X_new,req$r_x)[order(req$X_new),]
  lines(data[,1],data[,2],col=color[[j]],lwd=2)
}



legend(2,-2, c("y=sin(X)",'h=1.5','h=1','h=0.5','h=0.1','h=0.05'),text.col=c('gray70','blue','indianred1','mediumorchid3','salmon3','bisque1'))


```

##  Local ploynomial regression (<font color=#800000>p=2</font>、n=50)

```{r,echo=FALSE,warning=FALSE,message=FALSE,results='hide'}

n=50
#X=rnorm(n,mean=0,sd=2)
#e=rnorm(n,mean=0,sd=1)
#Y=sin(X)+e  
p=2

plot(X,Y,xlab = "x",ylab = "Y",main = "Scatter plot(n=50)",xlim = c(min(X), max(X)),ylim=c(-6,6),pch=20)
eq = function(X){sin(X)}
curve(eq, from=min(X),to=max(X),add = TRUE,lwd=4,col='gray70')


h=c(1.5,1,0.5,0.1,0.05)
color=list('blue','indianred1','mediumorchid3','salmon3','bisque1')

for(j in 1:5){
  ##
  Y_new=0
  X_new=seq(min(X),max(X),0.1)
  
  req=local_ploy_reg(X_new,k_f,h[j],X,Y,p)

  data=cbind(req$X_new,req$r_x)[order(req$X_new),]
  lines(data[,1],data[,2],col=color[[j]],lwd=2)
}



legend(2,-2, c("y=sin(X)",'h=1.5','h=1','h=0.5','h=0.1','h=0.05'),text.col=c('gray70','blue','indianred1','mediumorchid3','salmon3','bisque1'))



```

##  Local ploynomial regression (<font color=#800000>p=0</font>、n=100)

```{r,echo=FALSE,warning=FALSE,message=FALSE,results='hide'}
n=100
X=rnorm(n,mean=0,sd=2)
e=rnorm(n,mean=0,sd=1)
Y=sin(X)+e  
p=0

plot(X,Y,xlab = "x",ylab = "Y",main = "Scatter plot(n=100)",xlim = c(min(X), max(X)),ylim=c(-6,6),pch=20)
eq = function(X){sin(X)}
curve(eq, from=min(X),to=max(X),add = TRUE,lwd=4,col='gray70')


h=c(1.5,1,0.5,0.1,0.05)
color=list('blue','indianred1','mediumorchid3','salmon3','bisque1')

for(j in 1:5){
  ##
  Y_new=0
  X_new=seq(min(X),max(X),0.1)
  
  req=local_ploy_reg(X_new,k_f,h[j],X,Y,p)

  data=cbind(req$X_new,req$r_x)[order(req$X_new),]
  lines(data[,1],data[,2],col=color[[j]],lwd=2)
}



legend(2,-2, c("y=sin(X)",'h=1.5','h=1','h=0.5','h=0.1','h=0.05'),text.col=c('gray70','blue','indianred1','mediumorchid3','salmon3','bisque1'))



```

##  Local ploynomial regression (<font color=#800000>p=1</font>、n=100)

```{r,echo=FALSE,warning=FALSE,message=FALSE,results='hide'}
n=100
#X=rnorm(n,mean=0,sd=2)
#e=rnorm(n,mean=0,sd=1)
#Y=sin(X)+e  
p=1

plot(X,Y,xlab = "x",ylab = "Y",main = "Scatter plot(n=100)",xlim = c(min(X), max(X)),ylim=c(-6,6),pch=20)
eq = function(X){sin(X)}
curve(eq, from=min(X),to=max(X),add = TRUE,lwd=4,col='gray70')


h=c(1.5,1,0.5,0.1,0.05)
color=list('blue','indianred1','mediumorchid3','salmon3','bisque1')

for(j in 1:5){
  ##
  Y_new=0
  X_new=seq(min(X),max(X),0.1)
  
  req=local_ploy_reg(X_new,k_f,h[j],X,Y,p)

  data=cbind(req$X_new,req$r_x)[order(req$X_new),]
  lines(data[,1],data[,2],col=color[[j]],lwd=2)
}



legend(2,-2, c("y=sin(X)",'h=1.5','h=1','h=0.5','h=0.1','h=0.05'),text.col=c('gray70','blue','indianred1','mediumorchid3','salmon3','bisque1'))



```

##  Local ploynomial regression (<font color=#800000>p=2</font>、n=100)

```{r,echo=FALSE,warning=FALSE,message=FALSE,results='hide'}
n=100
#X=rnorm(n,mean=0,sd=2)
#e=rnorm(n,mean=0,sd=1)
#Y=sin(X)+e  
p=2

plot(X,Y,xlab = "x",ylab = "Y",main = "Scatter plot(n=100)",xlim = c(min(X), max(X)),ylim=c(-6,6),pch=20)
eq = function(X){sin(X)}
curve(eq, from=min(X),to=max(X),add = TRUE,lwd=4,col='gray70')


h=c(1.5,1,0.5,0.1,0.05)
color=list('blue','indianred1','mediumorchid3','salmon3','bisque1')

for(j in 1:5){
  ##
  Y_new=0
  X_new=seq(min(X),max(X),0.1)
  
  req=local_ploy_reg(X_new,k_f,h[j],X,Y,p)

  data=cbind(req$X_new,req$r_x)[order(req$X_new),]
  lines(data[,1],data[,2],col=color[[j]],lwd=2)
}



legend(2,-2, c("y=sin(X)",'h=1.5','h=1','h=0.5','h=0.1','h=0.05'),text.col=c('gray70','blue','indianred1','mediumorchid3','salmon3','bisque1'))



```


##  Local ploynomial regression (<font color=#800000>p=0</font>、n=200)

```{r,echo=FALSE,warning=FALSE,message=FALSE,results='hide'}
n=200
X=rnorm(n,mean=0,sd=2)
e=rnorm(n,mean=0,sd=1)
Y=sin(X)+e  
p=0

plot(X,Y,xlab = "x",ylab = "Y",main = "Scatter plot(n=200)",xlim = c(min(X), max(X)),ylim=c(-6,6),pch=20)
eq = function(X){sin(X)}
curve(eq, from=min(X),to=max(X),add = TRUE,lwd=4,col='gray70')
h=c(1.5,1,0.5,0.1,0.05)
color=list('blue','indianred1','mediumorchid3','salmon3','bisque1')

for(j in 1:5){
  ##
  Y_new=0
  X_new=seq(min(X),max(X),0.1)
  
  req=local_ploy_reg(X_new,k_f,h[j],X,Y,p)

  data=cbind(req$X_new,req$r_x)[order(req$X_new),]
  lines(data[,1],data[,2],col=color[[j]],lwd=2)
}



legend(2,-2, c("y=sin(X)",'h=1.5','h=1','h=0.5','h=0.1','h=0.05'),text.col=c('gray70','blue','indianred1','mediumorchid3','salmon3','bisque1'))



```

##  Local ploynomial regression (<font color=#800000>p=1</font>、n=200)

```{r,echo=FALSE,warning=FALSE,message=FALSE,results='hide'}
n=200
#X=rnorm(n,mean=0,sd=2)
#e=rnorm(n,mean=0,sd=1)
#Y=sin(X)+e  
p=1

plot(X,Y,xlab = "x",ylab = "Y",main = "Scatter plot(n=200)",xlim = c(min(X), max(X)),ylim=c(-6,6),pch=20)
eq = function(X){sin(X)}
curve(eq, from=min(X),to=max(X),add = TRUE,lwd=4,col='gray70')


h=c(1.5,1,0.5,0.1,0.05)
color=list('blue','indianred1','mediumorchid3','salmon3','bisque1')

for(j in 1:5){
  ##
  Y_new=0
  X_new=seq(min(X),max(X),0.1)
  
  req=local_ploy_reg(X_new,k_f,h[j],X,Y,p)

  data=cbind(req$X_new,req$r_x)[order(req$X_new),]
  lines(data[,1],data[,2],col=color[[j]],lwd=2)
}



legend(2,-2, c("y=sin(X)",'h=1.5','h=1','h=0.5','h=0.1','h=0.05'),text.col=c('gray70','blue','indianred1','mediumorchid3','salmon3','bisque1'))



```

##  Local ploynomial regression (<font color=#800000>p=2</font>、n=200)

```{r,echo=FALSE,warning=FALSE,message=FALSE,results='hide'}
n=200
#X=rnorm(n,mean=0,sd=2)
#e=rnorm(n,mean=0,sd=1)
#Y=sin(X)+e  
p=2

plot(X,Y,xlab = "x",ylab = "Y",main = "Scatter plot(n=200)",xlim = c(min(X), max(X)),ylim=c(-6,6),pch=20)
eq = function(X){sin(X)}
curve(eq, from=min(X),to=max(X),add = TRUE,lwd=4,col='gray70')


h=c(1.5,1,0.5,0.1,0.05)
color=list('blue','indianred1','mediumorchid3','salmon3','bisque1')

for(j in 1:5){
  ##
  Y_new=0
  X_new=seq(min(X),max(X),0.1)
  
  req=local_ploy_reg(X_new,k_f,h[j],X,Y,p)

  data=cbind(req$X_new,req$r_x)[order(req$X_new),]
  lines(data[,1],data[,2],col=color[[j]],lwd=2)
}



legend(2,-2, c("y=sin(X)",'h=1.5','h=1','h=0.5','h=0.1','h=0.05'),text.col=c('gray70','blue','indianred1','mediumorchid3','salmon3','bisque1'))



```

## how to choose h

##  leave-one-out cross validation score 

$$CV=\hat{R}(h)=\frac{1}{n}\sum_{i=1}^{n}\left(Y_i-\hat{r}_{(-i)}(x_i)\right)^2$$
```{r}
#### Local ploynomial regression with cv_1
local_ploy_reg.cv_1=function(X,Y,local_ploy_reg,h){
  
  R=0
  for(k in 1 :length(X)){
    data=cbind(X,Y) 
    X_d1=data[-k,] 
    req=local_ploy_reg(X[k],k_f,h,X_d1[,1],X_d1[,2],p)
    # RISK
    R[k]=(Y[k]-req$r_x)^2
  }
  
  cv_score=mean(R)
  result=list(cv_score=cv_score,h=h)
  return(result)
  
}
```

## n=200、p=1 、choose h=?


```{r,echo=FALSE,warning=FALSE,message=FALSE,results='hide'}
# data
set.seed(123)
n=200
X=rnorm(n,mean=0,sd=2)
e=rnorm(n,mean=0,sd=1)
Y=sin(X)+e  
p=1
```

```{r,echo=FALSE,warning=FALSE,message=FALSE,results='hide',cache=TRUE}

############### choose h #################
h=seq(0,1.5,.01)
h_list=0
risk_list=0

for(j in 1:length(h)){
  req_cv=local_ploy_reg.cv_1(X,Y,local_ploy_reg,h[j])
  h_list[j]=req_cv$h
  risk_list[j]=req_cv$cv_score
}

plot(h_list,risk_list,xlab = 'h',ylab = 'CV score',main='leave-one-out CV', type = "l",col='cyan4',lwd=2)
points(h[which.min(risk_list)],min(risk_list),col='coral2',pch=20,cex=2)
text(h[which.min(risk_list)],min(risk_list)+(max(risk_list)/10),paste('h=',h[which.min(risk_list)],'  cv=',round(min(risk_list),3)))

```

## n=200、p=1
```{r,echo=FALSE,warning=FALSE,message=FALSE,results='hold',cache=TRUE}
print(paste('h=',h[which.min(risk_list)]))
```

```{r,echo=FALSE,warning=FALSE,message=FALSE,results='hide',cache=TRUE}


plot(X,Y,xlab = "x",ylab = "Y",main = "Scatter plot(leave-one-out CV)",xlim = c(min(X), max(X)),ylim=c(-6,6),pch=20)
eq = function(X){sin(X)}
curve(eq, from=min(X),to=max(X),add = TRUE,lwd=4,col='gray70')

##############################

h_cv1=h[which.min(risk_list)]
score_cv1=min(risk_list)


Y_new=0
X_new=seq(min(X),max(X),0.1)
req=local_ploy_reg(X_new,k_f,h_cv1,X,Y,p)
data=cbind(req$X_new,req$r_x)[order(req$X_new),]
lines(data[,1],data[,2],col='cornflowerblue',lwd=2)
text(-4,4,paste('h=',h[which.min(risk_list)],'  cv=',round(min(risk_list),3)),col = 'cornflowerblue')

```


##  generalized cross validation score 

$$v=tr(L)$$
$$GCV(h)=\sum_{i=1}^{n}\left(\frac{Y_i-\hat{r}_n(x_i)}{1-\frac{v}{n}}\right)^2$$
```{r}
#### GCV

local_ploy_reg_GCV=function(k_f,h,X,Y,p){
  
  X_new=X
  n=length(X)
  r_x=0
  L=matrix(NaN,n,n)
  
  
  for(i in 1:length(X_new)){
    
    #############################
    #   X_x   
    #   W_x  
    X_x=matrix(NaN,n,(p+1)) # X_x 
    W_x=diag(NaN,n,n) # W_x 
    
    
    for(r in 1:n){
      
      for(c in 1:(p+1)){
        X_x[r,c]=(((X[r]-X_new[i])^(c-1))/factorial(c-1))
      }
      
      W_x[r,r]=k_f((X[r]-X_new[i])/h)
    }  
    ##################################
    # 例外處理
    
    
    tryCatch({
      
      ### l(x).trans
      e_T=append(1,rep(0,p))
      l_X_T=e_T%*%solve(t(X_x)%*% W_x%*%X_x)%*%t(X_x)%*%W_x
      
      ### r(x)
      r_x[i]= l_X_T%*%Y
      
      ### L --smoothing matrix
      L[i,]=l_X_T
    },error = function(err) {
      print(paste("ERROR:  ",err)) 
      print(i)
    })
    
  }
  tryCatch({
    
  GCV_value=mean(((Y-r_x)/(1-(sum(diag(L))/n)))^2)
  
  },error = function(err) {
    print(paste("ERROR:  ",err)) 
    print(i)
  })
  
  
  result=list(h=h,GCV_value=GCV_value)
  return(result)
}
```



## n=200、p=1 、choose h=?

```{r,echo=FALSE,warning=FALSE,message=FALSE,results='hide',cache=TRUE}


############### choose h #################
h=seq(0,1.5,.01)
h_list=0
risk_list=0

for(j in 1:length(h)){
  req_gcv=local_ploy_reg_GCV(k_f,h[j],X,Y,p)
  h_list[j]=req_gcv$h
  risk_list[j]=req_gcv$GCV_value
}


plot(h_list,risk_list,xlab = 'h',ylab = 'cv score',main='Generalized CV ', type = "l",col='cyan4',lwd=2)

points(h[which(risk_list==min(risk_list, na.rm = TRUE))],min(risk_list,na.rm = TRUE),col='coral2',pch=20,cex=2)

text(h[which(risk_list==min(risk_list, na.rm = TRUE))],
     min(risk_list,na.rm = TRUE)+(max(risk_list,na.rm = TRUE)/50),
     paste('h=',h[which(risk_list==min(risk_list, na.rm = TRUE))],'  CV=',round(min(risk_list,na.rm = TRUE),3)))

```


## n=200、p=1

```{r,echo=FALSE,warning=FALSE,message=FALSE,results='hold',cache=TRUE}
print(paste('h=',h[which(risk_list==min(risk_list, na.rm = TRUE))]))
```

```{r,echo=FALSE,warning=FALSE,message=FALSE,results='hide',cache=TRUE}

plot(X,Y,xlab = "x",ylab = "Y",main = "Scatter plot(Generalized CV)",xlim = c(min(X), max(X)),ylim=c(-6,6),pch=20)
eq = function(X){sin(X)}
curve(eq, from=min(X),to=max(X),add = TRUE,lwd=4,col='gray70')

##############################

h_gcv=h[which(risk_list==min(risk_list, na.rm = TRUE))]
score_gcv=min(risk_list, na.rm = TRUE)
  
Y_new=0
X_new=seq(min(X),max(X),0.1)
req=local_ploy_reg(X_new,k_f,h_gcv,X,Y,p)
data=cbind(req$X_new,req$r_x)[order(req$X_new),]
lines(data[,1],data[,2],col='hotpink3',lwd=2)
text(0,4,paste('h=',h[which(risk_list==min(risk_list, na.rm = TRUE))],'  CV=',round(min(risk_list,na.rm = TRUE),3)),col = 'hotpink3')

```


## <font color=#800000>leave-one-out</font>  v.s. <font color="#000066">GCV</font>(n=200、p=1)

```{r,echo=FALSE,warning=FALSE,message=FALSE,results='hide',cache=TRUE}
### data

plot(X,Y,xlab = "x",ylab = "Y",main = "Scatter plot( n=200、p=1)",xlim = c(min(X), max(X)),ylim=c(-6,6),pch=20)
eq = function(X){sin(X)}
curve(eq, from=min(X),to=max(X),add = TRUE,lwd=4,col='gray70')

#############################################

Y_new=0
X_new=seq(min(X),max(X),0.1)
req=local_ploy_reg(X_new,k_f,h_cv1,X,Y,p)
data=cbind(req$X_new,req$r_x)[order(req$X_new),]
lines(data[,1],data[,2],col='cornflowerblue',lwd=2)


##########################################

Y_new=0
X_new=seq(min(X),max(X),0.1)
req=local_ploy_reg(X_new,k_f,h_gcv,X,Y,p)
data=cbind(req$X_new,req$r_x)[order(req$X_new),]
lines(data[,1],data[,2],col='hotpink3',lwd=2)

########################################



legend(1,-4,c('y=sinx',paste('h=',h_cv1,'  CV=',round(score_cv1,3),'(CV_1)'),   paste('h=',h_gcv,'  CV=',round(score_gcv,3),'(GCV)')),
text.col=c('gray70','cornflowerblue','hotpink3'),cex=1.4)


```

##

$h=C n^{\frac{-1}{5}}$

```{r,echo=FALSE,warning=FALSE,message=FALSE,results='hide',cache=TRUE}

### data

plot(X,Y,xlab = "x",ylab = "Y",main = "Scatter plot( n=200、p=1)",xlim = c(min(X), max(X)),ylim=c(-6,6),pch=20)
eq = function(X){sin(X)}
curve(eq, from=min(X),to=max(X),add = TRUE,lwd=4,col='gray70')


C=c(1,2,5,10)
color=list('blue','indianred1','mediumorchid3','salmon3')

for(j in 1:4){
  ##
  Y_new=0
  h=C[j]*(n)^(-1/5)
  X_new=seq(min(X),max(X),0.1)
  
  req=local_ploy_reg(X_new,k_f,h,X,Y,p)

  data=cbind(req$X_new,req$r_x)[order(req$X_new),]
  lines(data[,1],data[,2],col=color[[j]],lwd=2)
}



legend(2,-2, c("y=sin(X)",paste('C=1','h=',round(1*(n)^(-1/5),3)),paste('C=2','h=',round(2*(n)^(-1/5),3)),paste('C=5','h=',round(5*(n)^(-1/5),3)),paste('C=10','h=',round(10*(n)^(-1/5)),3)),text.col=c('gray70','blue','indianred1','mediumorchid3','salmon3'))

```



## about p & h


## n=200、p=0 & p=1 ( fix h=1.5、1 )
```{r,echo=FALSE,warning=FALSE,message=FALSE,results='hide',cache=TRUE}

n=200
X=rnorm(n,mean=0,sd=2)
e=rnorm(n,mean=0,sd=1)
Y=sin(X)+e  
```


```{r,echo=FALSE,warning=FALSE,message=FALSE,results='hide',cache=TRUE}

plot(X,Y,xlab = "x",ylab = "Y",main = "Scatter plot(n=200)",xlim = c(min(X), max(X)),ylim=c(-6,6),pch=20)
eq = function(X){sin(X)}
curve(eq, from=min(X),to=max(X),add = TRUE,lwd=4,col='gray70')
###################################
h=c(1.5,1)
color1=list('dodgerblue4','orangered2')
color2=list('lightskyblue','salmon1')

#p=0
p=0
for(j in 1:2){
  ##
  Y_new=0
  X_new=seq(min(X),max(X),0.1)
  
  req=local_ploy_reg(X_new,k_f,h[j],X,Y,p)
  
  data=cbind(req$X_new,req$r_x)[order(req$X_new),]
  lines(data[,1],data[,2],col=color1[[j]],lwd=2)
}

p=1
for(j in 1:2){
  ##
  Y_new=0
  X_new=seq(min(X),max(X),0.1)
  
  req=local_ploy_reg(X_new,k_f,h[j],X,Y,p)
  
  data=cbind(req$X_new,req$r_x)[order(req$X_new),]
  lines(data[,1],data[,2],col=color2[[j]],lwd=2)
}


legend(2,-2, c("y=sin(X)",'p=0、h=1.5','p=0、h=1','p=1、h=1.5','p=1、h=1'),text.col=c('gray70','dodgerblue4','orangered2','lightskyblue','salmon1'))

```


## n=200、p=0、1、2、3 ( fix h=1 )

```{r,echo=FALSE,warning=FALSE,message=FALSE,results='hide',cache=TRUE}

plot(X,Y,xlab = "x",ylab = "Y",main = "Scatter plot(n=200)",xlim = c(min(X), max(X)),ylim=c(-6,6),pch=20)
eq = function(X){sin(X)}
curve(eq, from=min(X),to=max(X),add = TRUE,lwd=4,col='gray70')
###################################
h=1
color1=list('dodgerblue4','orangered2')
color2=list('lightskyblue','salmon1')

#p=0
p=0
for(j in 1:1){
  ##
  Y_new=0
  X_new=seq(min(X),max(X),0.1)
  
  req=local_ploy_reg(X_new,k_f,h[j],X,Y,p)
  
  data=cbind(req$X_new,req$r_x)[order(req$X_new),]
  lines(data[,1],data[,2],col='dodgerblue4',lwd=2)
}

p=1
for(j in 1:1){
  ##
  Y_new=0
  X_new=seq(min(X),max(X),0.1)
  
  req=local_ploy_reg(X_new,k_f,h[j],X,Y,p)
  
  data=cbind(req$X_new,req$r_x)[order(req$X_new),]
  lines(data[,1],data[,2],col='orangered2',lwd=2)
}


p=2
for(j in 1:1){
  ##
  Y_new=0
  X_new=seq(min(X),max(X),0.1)
  
  req=local_ploy_reg(X_new,k_f,h[j],X,Y,p)
  
  data=cbind(req$X_new,req$r_x)[order(req$X_new),]
  lines(data[,1],data[,2],col='lightskyblue',lwd=2)
}



p=3
for(j in 1:1){
  ##
  Y_new=0
  X_new=seq(min(X),max(X),0.1)
  
  req=local_ploy_reg(X_new,k_f,h[j],X,Y,p)
  
  data=cbind(req$X_new,req$r_x)[order(req$X_new),]
  lines(data[,1],data[,2],col='salmon1',lwd=2)
}




legend(2,-2, c("y=sin(X)",'p=0、h=1','p=1、h=1','p=2、h=1','p=3、h=1'),text.col=c('gray70','dodgerblue4','orangered2','lightskyblue','salmon1'))

```

## n=200 、p=0 & p=1 (USE GCV SCORE TO CHOOSE THE BEST H)

```{r,echo=FALSE,warning=FALSE,message=FALSE,results='hide',cache=TRUE}


plot(X,Y,xlab = "x",ylab = "Y",main = "Scatter plot(n=200)",xlim = c(min(X), max(X)),ylim=c(-6,6),pch=20)
eq = function(X){sin(X)}
curve(eq, from=min(X),to=max(X),add = TRUE,lwd=4,col='gray70')

############### choose h #################

#p=0

h=seq(0,1.5,.01)
p=0
h_list=0
risk_list=0

for(j in 1:length(h)){
  req_gcv=local_ploy_reg_GCV(k_f,h[j],X,Y,p)
  h_list[j]=req_gcv$h
  risk_list[j]=req_gcv$GCV_value}

h_gcv_p_0=h[which(risk_list==min(risk_list, na.rm = TRUE))]
score_gcv_p_0= min(risk_list, na.rm = TRUE)

############# fit #############################

Y_new=0
X_new=seq(min(X),max(X),0.1)
req=local_ploy_reg(X_new,k_f,h_gcv_p_0,X,Y,p)
data=cbind(req$X_new,req$r_x)[order(req$X_new),]
lines(data[,1],data[,2],col='orangered',lwd=2)


# p=1

h=seq(0,1.5,.01)
p=1
h_list=0
risk_list=0

for(j in 1:length(h)){
  req_gcv=local_ploy_reg_GCV(k_f,h[j],X,Y,p)
  h_list[j]=req_gcv$h
  risk_list[j]=req_gcv$GCV_value}

h_gcv_p_1=h[which(risk_list==min(risk_list, na.rm = TRUE))]
score_gcv_p_1= min(risk_list, na.rm = TRUE)

############# fit #############################

Y_new=0
X_new=seq(min(X),max(X),0.1)
req=local_ploy_reg(X_new,k_f,h_gcv_p_1,X,Y,p)
data=cbind(req$X_new,req$r_x)[order(req$X_new),]
lines(data[,1],data[,2],col='pink4',lwd=2)


# p=2

h=seq(0,1.5,.01)
p=2
h_list=0
risk_list=0

for(j in 1:length(h)){
  req_gcv=local_ploy_reg_GCV(k_f,h[j],X,Y,p)
  h_list[j]=req_gcv$h
  risk_list[j]=req_gcv$GCV_value}

h_gcv_p_2=h[which(risk_list==min(risk_list, na.rm = TRUE))]
score_gcv_p_2= min(risk_list, na.rm = TRUE)

############# fit #############################


# p=3

h=seq(0,1.5,.01)
p=3
h_list=0
risk_list=0

for(j in 1:length(h)){
  req_gcv=local_ploy_reg_GCV(k_f,h[j],X,Y,p)
  h_list[j]=req_gcv$h
  risk_list[j]=req_gcv$GCV_value}

h_gcv_p_3=h[which(risk_list==min(risk_list, na.rm = TRUE))]
score_gcv_p_3= min(risk_list, na.rm = TRUE)

############# fit #############################




###########################
legend(2,-3,c('y=sinx',paste('p=0','h=',h_gcv_p_0,' GCV=',round(score_gcv_p_0,3)),paste('p=1','h=',h_gcv_p_1,' GCV=',round(score_gcv_p_1,3))),text.col = c('gray70','orangered','pink4'))

```


## n=200 、p=0、1、2、3 (USE GCV SCORE TO CHOOSE THE BEST H)
```{r,echo=FALSE,warning=FALSE,message=FALSE,results='hide',cache=TRUE}


plot(X,Y,xlab = "x",ylab = "Y",main = "Scatter plot(n=200)",xlim = c(min(X), max(X)),ylim=c(-6,6),pch=20)
eq = function(X){sin(X)}
curve(eq, from=min(X),to=max(X),add = TRUE,lwd=4,col='gray70')

############### choose h #################

#p=0

Y_new=0
X_new=seq(min(X),max(X),0.1)
req=local_ploy_reg(X_new,k_f,h_gcv_p_0,X,Y,p)
data=cbind(req$X_new,req$r_x)[order(req$X_new),]
lines(data[,1],data[,2],col='orangered',lwd=2)


# p=1


Y_new=0
X_new=seq(min(X),max(X),0.1)
req=local_ploy_reg(X_new,k_f,h_gcv_p_1,X,Y,p)
data=cbind(req$X_new,req$r_x)[order(req$X_new),]
lines(data[,1],data[,2],col='pink4',lwd=2)


# p=2


Y_new=0
X_new=seq(min(X),max(X),0.1)
req=local_ploy_reg(X_new,k_f,h_gcv_p_2,X,Y,p)
data=cbind(req$X_new,req$r_x)[order(req$X_new),]
lines(data[,1],data[,2],col='royalblue1',lwd=2)



# p=3


Y_new=0
X_new=seq(min(X),max(X),0.1)
req=local_ploy_reg(X_new,k_f,h_gcv_p_3,X,Y,p)
data=cbind(req$X_new,req$r_x)[order(req$X_new),]
lines(data[,1],data[,2],col='palegreen4',lwd=2)


###########################
legend(2,-3,c('y=sinx',paste('p=0','h=',h_gcv_p_0,' GCV=',round(score_gcv_p_0,3)),paste('p=1','h=',h_gcv_p_1,' GCV=',round(score_gcv_p_1,3)),paste('p=2','h=',h_gcv_p_2,' GCV=',round(score_gcv_p_2,3)),paste('p=3','h=',h_gcv_p_3,' GCV=',round(score_gcv_p_3,3))),text.col = c('gray70','orangered','pink4','royalblue1','palegreen4'))

```

